### 2012-01-30 docs/getting_started/getting_started.tex
more quickstart

\item Get a copy of \boxlib.

@@

\item Setup your shell environment.

@@

If your shell is{\tt Csh/Tcsh}, add
\begin{verbatim}
setenv BOXLIB_HOME /path/to/BoxLib/
\end{verbatim}
to your {\tt .cshrc}.

\item Setup the problem's {\tt GNUmakefile}.

@@

We only need to worry about the options at the very top of the
{\tt GNUmakefile} for now.  These should be set as follows:
\begin{itemize}
\item {\tt NDEBUG := t}

@@

\item Build the executable.

@@

\item Copy in auxillary files.

@@

\item Run.

@@

\item Examine the output.

@@

\subsection{\tt Amrvis}

{\tt Amrvis} is an easy-to-use visualization tool developed at LBL for
2- and 3D datasets which can plot slices through 3D datasets as well
as volume-renderings.  It can also very easily extract 1D lines
through the dataset along any coordinate direction.  It is distributed
separately from the \maestro\ distribution.

@@

\subsection{VisIt}

VisIt is a powerful, DOE-supported visualization tool for 2- and 3D
datasets.  It can do contouring, volume rendering, streamlines, ...\
directly from \boxlib\ plotfiles (to open a plotfile in VisIt, point to
the {\tt Header} file inside the plotfile directory).  Details on
visit can be found at {\tt https://wci.llnl.gov/codes/visit/home.html}\,.

>>>>

\item {\em Get a copy of \boxlib}.

@@

\item {\em Setup your shell environment}.

@@

If your shell is {\tt Csh/Tcsh}, add
\begin{verbatim}
setenv BOXLIB_HOME /path/to/BoxLib/
\end{verbatim}
to your {\tt .cshrc}.

\item {\em Setup the problem's {\tt GNUmakefile}}.

@@

Change directory to {\tt MAESTRO/test2/}.    
We only need to worry about the options at the very top of the
{\tt GNUmakefile} for now.  These should be set as follows:
\begin{itemize}
\item {\tt NDEBUG := t}

@@

\item {\em Build the executable}.

@@

\item {\em Copy in auxillary files}.

@@

\item {\em Run!}

@@

\item {\em Examine the output}.

@@

\subsection{\amrvis}

\amrvis\ is an easy-to-use visualization tool developed at LBL for
2- and 3D datasets which can plot slices through 3D datasets as well
as volume-renderings.  It can also very easily extract 1D lines
through the dataset along any coordinate direction.  It is distributed
separately from the \maestro\ distribution.

\amrvis\ can be obtained via git as:
\begin{verbatim}
git clone https://ccse.lbl.gov/pub/Downloads/Amrvis.git
\end{verbatim}
\amrvis\ is built in the C++ \boxlib\ framework (instead of the Fortran 
\boxlib\ framework that \maestro\ uses).  The build systems are similar,
but differ in a few ways.

\amrvis\ uses the {\tt Motif} library for defining the GUI.  On a Linux 
system, you may need to install the {\tt lesstif} package and any
related development packages (e.g.\ {\tt lesstif-devel}).  Depending
on your Linux system, you may also need to install {\tt libXpm} 
and related development packages (e.g.\ {\tt libXpm-devel}).

%need to modify _f95_lib

library line

@@

There is also a python visualization method in {\tt
fParallel/data\_processing/python\_plotfile}.  This is described
in \S~\ref{sec:vis:python}.

\subsection{\visit}

\visit\ is a powerful, DOE-supported visualization tool for 2- and 3D
datasets.  It can do contouring, volume rendering, streamlines, ...\
directly from \boxlib\ plotfiles (to open a plotfile in \visit, point to
the {\tt Header} file inside the plotfile directory).  Details on
\visit\ can be found at:\newline
 {\tt https://wci.llnl.gov/codes/visit/home.html}\,. \newline
The easiest way to get started with \visit\ is to download a precompiled
binary from the \visit\ webpage.

Once \visit\ is installed, you can open a \boxlib\ plotfile by pointing
\visit\ to the {\tt Header} file in the plotfile directory.
